Supporting Information

### 2017-02-09 code/rmarkdown/supporting-information.Rmd
benchmark analysis results figure

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap='insert caption here.'}
plot(1)
```

>>>>

```{r, echo=FALSE, message=FALSE, fig.height=5.0, fig.width=4.5, fig.cap='Benchmark analysis. Boxplots show the amount of time required to solve a problem under a given set of parameters. Note that times are shown on a log_{10} scale.'}
# prepare data
plot.DF <- benchmark.DF %>%
  mutate(blm = paste0('BLM = ',blm)) %>% 
  mutate(number.features=factor(number.features)) %>%
  mutate(formulation = paste0(formulation, ' formulation')) %>%
  mutate(number.planning.units=factor(number.planning.units))
# make plot
ggplot(plot.DF, aes(x=number.planning.units, y=time, color=number.features)) +
  geom_boxplot() +
  facet_grid(blm ~ formulation ) +
  scale_y_continuous(trans='log10') +
  xlab('Number of planning units') + ylab('Solve time (s)') +
  labs(color='Number of features') +
  theme(axis.line.x=element_line(), axis.line.y=element_line(),
    strip.background = element_rect(fill='grey20'),
    strip.text = element_text(color='white', size=12),
    legend.position='bottom')
```
